---
title: "rsv_inter_ew"
author: "David Hodgson"
date: "24/09/2020"
output: html_document
---


# 1. Setup 
# 1.1 Import libraries
May need to downoad all of these (use install.packages)
```{r libraries}

library(Rcpp)       # For c++ intergration
library(RcppEigen)  # Ditto
library(coda)       # Ditto
library(tidyverse)
library(parallel)
library(MASS)
library(foreach)
library(gridExtra)
library(doParallel)
library(BayesianTools)
library(devtools)
library(here)
library(patchwork)
#source( here::here("src", "helpers.R")) #ensure c++14 is enabled

```


## 2 Import data for the epidemic model intervention model
### 2.1 RunIntervention class

This section calls a class from the cpp module inteface (RunInterventions.cpp) for the cpp intervention model (defined in RunInterventions.h).
Then, using demographic data from the UK (ukdata) and model data needed for the intervention programmes (data_inter_uk), the intervention model class is initialised and ready to use! 

```{r}

sourceCpp(here("src", "RunInterventions.cpp")) # Uploads empty RunInterventions class
source(here("R", "RunInterventionsClass.R")) # Uploads emmake_RunInterventionspty function
burnin_yrs <- 2
run_yrs <- 10

# Load premade datasets
load(file = here::here("data", "inter_model_input", "rsv_data_uk.RData")) # loads ukdata
load(file = here::here("data", "inter_model_input", "inter_data_uk.RData")) # loads data_inter_uk

classRunInterventions <- make_RunInterventions(RunInterventions, ukdata, data_inter_uk, burnin_yrs * 365, run_yrs * 365)

```

# 3. Code to run custom RSV intervention programmes

Three examples of how to implement your own custom calendars are given below. 

```{r}

# Load relevant R scripts
source("R/vac_cal.R") # generates the vaccination calendars
source("R/calc_outcomes.R")  # calculate the outcomes
# Load posteriors
load(here("data", "inter_model_output", "posteriors.Rda"))  # posteriors from fitting in Hodgson et al. 2020
# Load seeds
seeds <- read.csv(here("data", "inter_model_input", "seed_samples.csv"), header = FALSE)[, 1] + 1

# Ex.1 Long-acting monoclonal antibodies at HR, LR, and VHR, given seasonally with 90% coverage.
ind_pal <- c(rep(1, 9), rep(0, 16)) # VHR (<8 months)
ind_mabs <- c(rep(1, 1), rep(0, 24)) # Birth only (0 months only)
mab_eff <- rweibull(1250, 11.8975, 0.7317) # efficacy of long-acting mabs
# VHR, HR and LR at birth during the winter
make_vac_program_info_custom_mabs <- function(seed) {
  list(
      mAB_VHR = list(id = TRUE, age_id = ind_pal, t_start = 15, t_end = 36, eff = mab_eff[seed], cov = 0.9),
      mAB_HR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 15, t_end = 36, eff = mab_eff[seed], cov = 0.9),
      mAB_LR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 15, t_end = 36, eff = mab_eff[seed], cov = 0.9)
    )
}

# Ex.2 LAV vaccination all <1 years (HR and LR) with palivizumab programme, iven seasonally woth 90% coverage
ind_pal <- c(rep(1, 9), rep(0, 16)) # VHR (<8 months)
ind_lav <- c(rep(1, 12), rep(0, 13)) # All under 1s
pal_eff <- rweibull(1250, 12.4311, 0.772251) # efficacy of palivizumab
lav_eff <- rweibull(1250, 31.4637, 0.844676) # efficacy of lav
make_vac_program_info_custom_LAV <- function(seed) {
  list(
      pal = list(id = TRUE, age_id = ind_pal, t_start = 15, t_end = 36, eff = pal_eff[seed], cov = 0.9),
      LAV_HR = list(id = TRUE, age_id = ind_lav, uptake_type = 2, t_start = 15, t_end = 36, eff = lav_eff[seed], cov = 0.9),
      LAV_LR = list(id = TRUE, age_id = ind_lav, uptake_type = 2, t_start = 15, t_end = 36, eff = lav_eff[seed], cov = 0.9)
    )
}

# Ex.3 Maternal vaccination all with Palivizumab given seasonally (July - Oct) with 60% coverage.
ind_pal <- c(rep(1, 9), rep(0, 16)) # VHR (<8 months)
ind_parents <- c(0,0,0,0,0,0,0,0,0,0,0,0,0, 0,   0,   0,   0,   0,   1.0,1.0,1.0,0,0,0,0) # 15-44 (parents)
pal_eff <- rweibull(1250, 12.4311, 0.772251) # efficacy of palivizumab
mat_eff <- rweibull(1250, 3.32676, 0.461343) # efficacy in neonates
lav_eff <- rweibull(1250, 31.4637, 0.844676) # efficacy in mothers
make_vac_program_info_custom_mats <- function(seed) {
  list(
      pal = list(id = TRUE, age_id = ind_pal, t_start = 15, t_end = 36, eff = pal_eff[seed], cov = 0.9),
      mat =  list(id = TRUE, age_id = ind_parents, t_start = 1, t_end = 21*7 + 1, eff_inf = mat_eff[seed], eff_mat = lav_eff[seed], cov = 0.6)
    )
}

vac_par_info <- list(om_mab = 1 / 250, direct = FALSE, xi_boost = 1)

output1 <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_mabs, vac_par_info, 0, post)
output2 <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_LAV, vac_par_info, 0, post)
output3 <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_mats, vac_par_info, 0.6, post)

```

## 4. Code to run just to get weekly outcomes by age group

```{r}

# Load relevant R scripts
source("R/vac_cal.R") # generates the vaccination calendars
source("R/calc_outcomes.R")  # calculate the outcomes
# Load posteriors
load(here("data", "inter_model_output", "posteriors.Rda"))  # posteriors from fitting in Hodgson et al. 2020
# Load seeds
seeds <- read.csv(here("data", "inter_model_input", "seed_samples.csv"), header = FALSE)[, 1] + 1

# DEFAULT Palivizumab programme only for Lucy Gregory
ind_pal <- c(rep(1, 9), rep(0, 16)) # VHR (<8 months)
pal_eff <- rweibull(1250, 12.4311, 0.772251) # efficacy of palivizumab
make_vac_program_info_custom_default <- function(seed) {
  list(
      pal = list(id = TRUE, age_id = ind_pal, t_start = 15, t_end = 36, eff = pal_eff[seed], cov = 0.9)
    )
}

vac_par_info <- list(om_mab = 1 / 250, direct = FALSE, xi_boost = 1)

output_default <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_default, vac_par_info, 0, post)
save(output_default, file = here("data", "inter_model_output", "status_quo.RData"))

```


```{r}

meanfiles <- output_default[[1]] %>%
  group_by(outcome, time, age_group) %>%
  dplyr::summarise(incidence = mean(incidence)) %>%
  mutate(time = time - 52*9) %>% as.data.frame

save(meanfiles, file = here("data", "inter_model_output", "status_quo_mean.RData"))

meanfiles %>% 
  filter(age_group == 1, outcome == "all_cases") %>%
  ggplot() + 
    geom_line(aes(x = time, y = incidence))

age_pop <- c(56605, 56605, 56605, 56605, 56605, 56605, 56605, 56605, 56605, 56605, 56605, 56605,
    679265, 679265, 679265, 679265, 3.396325e6, 3.396325e6, 6.79265e6, 6.79265e6, 6.79265e6, 6.79265e6,
    6.79265e6, 6.79265e6, 7.799725e6)

meanfiles_rate <- meanfiles %>% group_by(outcome, time) %>% mutate(rates = incidence / age_pop * 100000)


load(file = here("data", "inter_model_output", "status_quo_mean.RData"))

write.csv(meanfiles_rate, file = here("data", "inter_model_output", "status_quo_mean.csv"))

```