---
title: "rsv_inter_ew"
author: "David Hodgson"
date: "24/09/2020"
output: html_document
---


# 1. Setup 
# 1.1 Import libraries
May need to downoad all of these (use install.packages)
```{r libraries}

library(Rcpp)       # For c++ intergration
library(RcppEigen)  # Ditto
library(coda)       # Ditto
library(tidyverse)
library(parallel)
library(MASS)
library(foreach)
library(gridExtra)
library(doParallel)
library(BayesianTools)
library(devtools)
library(here)
library(patchwork)
library(triangle)


#source( here::here("src", "helpers.R")) #ensure c++14 is enabled

```


## 2 Import data for the epidemic model intervention model
### 2.1 RunIntervention class

This section calls a class from the cpp module inteface (RunInterventions.cpp) for the cpp intervention model (defined in RunInterventions.h).
Then, using demographic data from the UK (ukdata) and model data needed for the intervention programmes (data_inter_uk), the intervention model class is initialised and ready to use! 

```{r}

sourceCpp(here("src", "RunInterventions.cpp")) # Uploads empty RunInterventions class
source(here("R", "RunInterventionsClass.R")) # Uploads emmake_RunInterventionspty function
burnin_yrs <- 2
run_yrs <- 10

# Load premade datasets
load(file = here::here("data", "inter_model_input", "rsv_data_uk.RData")) # loads ukdata
load(file = here::here("data", "inter_model_input", "inter_data_uk.RData")) # loads data_inter_uk

classRunInterventions <- make_RunInterventions(RunInterventions, ukdata, data_inter_uk, burnin_yrs * 365, run_yrs * 365)

```

# 3. Code to run custom RSV intervention programmes

Three examples of how to implement your own custom calendars are given below. 

```{r}

source(here("R", "run_scripts.R")) # Uploads emmake_RunInterventionspty function
# make_data_list() do not rerun, will create new efficacy values and will consequently have to rerun everything

```

## 4. Code to run just to get weekly outcomes by age group

```{r}

source(here("R", "calc_outcomes.R")) # Uploads emmake_RunInterventionspty function
source(here("R", "vac_cal.R")) # Uploads emmake_RunInterventionspty function
source(here("R", "run_scripts.R")) # Uploads emmake_RunInterventionspty function


load(file = here::here("outputs", "nirsevimab", "data_list.RData")) # data_list
run_model_base(data_list)
run_model_base_direct(data_list)

# Calcualte ICERs
run_icer_base(20000, "base_icer")
run_icer_base(15000, "lower_icer")

```

## Look at estimating the dominance from these programmes

```{r}

source("R/cea.R")

load(file = here("outputs", "nirsevimab", "impact", "base", "none.RData")) # output_default_none
load(file = here("outputs", "nirsevimab", "impact", "base", "status_quo_base.RData")) # output_default_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_vhr_base.RData")) # output_season_vhr_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_base.RData")) # output_season_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_yr_base.RData")) # output_yr_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_catchup_base.RData")) # output_season_catchup_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_catchup_nip_base.RData")) # output_season_catchup_nip_base

get_cea_plane_info <- function(none, output, name) {
  pal_cost <- 4035.50

  mean_QALY_none <- none$QALY %>% filter(type == "discounted", metric == "total") %>% unique %>% pull(value) %>% mean(na.rm = TRUE) # qaly loss
  mean_cost_treat_none <- none$cost %>% filter(type == "discounted", metric == "total") %>% unique %>% pull(value) %>% mean(na.rm = TRUE)  # cost of treatment

  mean_QALY <- output$QALY %>% filter(type == "discounted", metric == "total") %>% unique %>% pull(value) %>% mean(na.rm = TRUE) # qaly loss
  mean_cost_treat <- output$cost %>% filter(type == "discounted", metric == "total") %>% unique %>% pull(value) %>% mean(na.rm = TRUE)  # cost of treatment
  mean_cost_ad <- (output$vac_cal[, 1] * pal_cost * exp(-(1:521 - 1) * 0.035 / 52.0)) %>% sum # cost of pal programmes
  doses <- (output$vac_cal[, 2] * exp(-(1:521 - 1) * 0.035 / 52.0)) %>% sum # number of doses of mabs given

  data.frame(
    strategy = name,
    QALY = mean_QALY_none - mean_QALY,
    cost = (mean_cost_treat + mean_cost_ad) - mean_cost_treat_none,
    doses = doses
  )
}

outputs <- list(output_season_vhr_base, output_season_base, output_yr_base, output_season_catchup_base, output_season_catchup_nip_base)
names <- list("vhr", "season", "year-round", "season + cathcup", "season + catchup + PID")
icer_table <- map2(outputs, names, ~get_cea_plane_info(output_default_base, .x, .y)) %>% bind_rows

plot_plane <- function(icer_table, ppd) {
  icer_table_cal <- icer_table %>% mutate(cost_total = cost + doses * ppd)
  icer_table_cal %>% 
    ggplot() +
      geom_point(aes(x = QALY, y = cost_total, color = strategy)) + 
      theme_bw()
     # geom_text(aes(x = QALY, y = cost_total, label = strategy))
}

plot_plane(icer_table, 30) # holds assuming price is at least £30

```

# Calculate purchasing price per dose
```{r}

# Sensitivity analysis
run_icer_mabs_dur(data_list, 20000)
run_icer_coverage(data_list, 20000, 0.7)
ind_mabs_2mo <- c(0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
run_icer_admin_year(data_list, 20000, ind_mabs_2mo)

```

# Calculate purchasing price per dose (FIG 1a)

```{r}

library(here)
load(file = here("outputs", "nirsevimab", "impact", "base", "none.RData")) # output_default_none
load(file = here("outputs", "nirsevimab", "impact", "base", "status_quo_base.RData")) # output_default_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_vhr_base.RData")) # output_season_vhr_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_base.RData")) # output_season_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_yr_base.RData")) # output_yr_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_catchup_base.RData")) # output_season_catchup_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_catchup_nip_base.RData")) # output_season_catchup_nip_base

get_new_data_frame <- function(df_outputs) {
  df_outputs$outcomes_week_age %>%
  group_by(outcome, seed) %>%
  summarise(tot_inci = sum(incidence))
}

get_change <- function(base, inter, string) {

  left_join(
    get_new_data_frame(base) %>% rename(tot_inci_base = tot_inci),
    get_new_data_frame(inter) %>% rename(tot_inci_output = tot_inci)
  )  %>% mutate(inci_averted = (tot_inci_base - tot_inci_output) / tot_inci_base, type = string) %>%
    filter(!is.na(inci_averted)) %>% as.data.frame
}

full_inter_outcomes <- bind_rows(
  get_change(output_default_base, output_season_vhr_base, "VHR"),
  get_change(output_default_base, output_season_base, "S"),
  get_change(output_default_base, output_yr_base, "YR"),
  get_change(output_default_base, output_season_catchup_base, "S-catchup"),
  get_change(output_default_base, output_season_catchup_nip_base, "S-catchup-pid")
) %>% mutate(type = factor(type, c("VHR", "S", "YR", "S-catchup", "S-catchup-pid"))) %>%
  filter(outcome != "all_cases") %>%
  mutate(outcome = factor(outcome, levels = c("symptomatic_cases", "gp_visits", "hospital_cases", "bed_days", "deaths"))) %>%
  mutate(outcome = case_when(
    outcome == "symptomatic_cases"~"Symptomatic cases",
    outcome == "gp_visits"~"GP consultations",
    outcome == "hospital_cases"~"Hospital cases",
    outcome == "bed_days"~"Bed days",
    outcome == "deaths"~"Deaths"
  )
  )  %>%
  mutate(type = factor(type, levels = c("VHR", "S", "YR", "S-catchup", "S-catchup-pid")))

require(ggdist)
p1A <- full_inter_outcomes %>%
  ggplot() + 
    stat_pointinterval(aes(y = outcome, x = inci_averted, color = outcome, point_fill = outcome), .width = c(0.95), size = 1,
      shape = 21, point_color = "black", point_size = 2, point_alpha = 0.8) + 
    facet_grid(rows = vars(type)) + 
    labs(x = "Proportion of total cases averted", y = "Healthcare outcome") + theme_bw() + theme(legend.position = "none")

type <- c("VHR", "S", "YR", "S-catchup", "S-catchup-pid")
tot_dose <- c(
  output_season_vhr_base$vac_cal[1:52, 2] %>% sum,
  output_season_base$vac_cal[1:52, 2] %>% sum,
  output_yr_base$vac_cal[1:52, 2] %>% sum,
  output_season_catchup_base$vac_cal[1:52, 2] %>% sum,
  output_season_catchup_nip_base$vac_cal[1:52, 2] %>% sum
)

dose_df <- data.frame(
  type = type, 
  tot_dose = tot_dose
)

full_inter_outcomes_doses <- full_inter_outcomes %>% left_join(dose_df, by = "type") %>% 
  mutate(capd = 1000 * (tot_inci_base - tot_inci_output) / tot_dose) %>% 
  mutate(type = factor(type, c("VHR", "S", "YR", "S-catchup", "S-catchup-pid")))



p1B <- full_inter_outcomes_doses %>%
  ggplot() + 
    stat_pointinterval(aes(y = outcome, x = capd, color = outcome, point_fill = outcome), .width = c(0.95), size = 1,
      shape = 21, point_color = "black", point_size = 2, point_alpha = 0.8) + 
    facet_grid(rows = vars(type)) + 
    labs(x = "Number of cases averted per 1000 doses", y = "Healthcare outcome") + theme_bw() + theme(legend.position = "none", 
    axis.text.y = element_blank(), axis.title.y = element_blank()) 


```

# Look athe indirect effects 
```{r}

library(here)
load(file = here("outputs", "nirsevimab", "impact", "base", "none.RData")) # output_default_none
load(file = here("outputs", "nirsevimab", "impact", "base", "status_quo_base.RData")) # output_default_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_vhr_base.RData")) # output_season_vhr_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_base.RData")) # output_season_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_yr_base.RData")) # output_yr_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_catchup_base.RData")) # output_season_catchup_base
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_catchup_nip_base.RData")) # output_season_catchup_nip_base

load(file = here("outputs", "nirsevimab", "impact", "base", "none_d.RData")) # output_default_none_d
load(file = here("outputs", "nirsevimab", "impact", "base", "status_quo_base_d.RData")) # output_default_base_d
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_vhr_base_d.RData")) # output_season_vhr_base_d
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_base_d.RData")) # output_season_base_d
load(file = here("outputs", "nirsevimab", "impact", "base", "output_yr_base_d.RData")) # output_yr_base_d
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_catchup_base_d.RData")) # output_season_catchup_base_d
load(file = here("outputs", "nirsevimab", "impact", "base", "output_season_catchup_nip_base_d.RData")) # output_season_catchup_nip_base_d


get_new_data_frame_age <- function(df_outputs) {
  df_outputs$outcomes_week_age %>%
    mutate(age_group_cat = case_when(
      (age_group >= 1) & (age_group <= 6)~"<6 mo",
      (age_group >= 7) & (age_group <= 12)~"6-11 mo",
      (age_group >= 13) & (age_group <= 16)~"1-4 yrs",
      (age_group >= 17) & (age_group <= 23)~"5-64 yrs",
      (age_group >= 24) & (age_group <= 25)~"65+ yrs"
      )) %>%
    group_by(outcome, seed, age_group_cat) %>%
    summarise(tot_inci = sum(incidence))
}

get_prob_direct_df <- function(base, inter, base_d, inter_d, string) {
    left_join(
      left_join(
        left_join(
          get_new_data_frame_age(base) %>% rename(tot_inci_base = tot_inci),
          get_new_data_frame_age(base_d) %>% rename(tot_inci_d_base = tot_inci)
        ),
        get_new_data_frame_age(inter) %>% rename(tot_inci_inter = tot_inci)
      ),
      get_new_data_frame_age(inter_d) %>% rename(tot_inci_d_inter = tot_inci)
    ) %>%  mutate(cases_averted_direct =  tot_inci_base - tot_inci_d_inter, cases_averted_indirect = tot_inci_d_inter - tot_inci_inter) %>%
    mutate(cases_averted_direct_prop = cases_averted_direct / sum(tot_inci_base), cases_averted_indirect_prop = cases_averted_indirect / sum(tot_inci_base)) %>% 
    mutate(name = string)
}

direct_df <- bind_rows(
  get_prob_direct_df(output_default_base, output_season_vhr_base, output_default_base_d, output_season_vhr_base_d, "VHR"),
  get_prob_direct_df(output_default_base, output_season_base, output_default_base_d, output_season_base_d, "S"),
  get_prob_direct_df(output_default_base, output_yr_base, output_default_base_d, output_yr_base_d, "YR"),
  get_prob_direct_df(output_default_base, output_season_catchup_base, output_default_base_d, output_season_catchup_base_d, "S-catchup"),
  get_prob_direct_df(output_default_base, output_season_catchup_nip_base, output_default_base_d, output_season_catchup_nip_base_d, "S-catchup-pid")
)

direct_df_summary <- direct_df %>% group_by(outcome, age_group_cat, name) %>%
  summarise(cases_averted_direct_prop = mean(cases_averted_direct_prop), cases_averted_indirect_prop = mean(cases_averted_indirect_prop)) %>%
  pivot_longer(c(cases_averted_direct_prop, cases_averted_indirect_prop), names_to = "aversion_type", values_to = "prop")

direct_df_summary_plt <- direct_df_summary %>%
  mutate(aversion_type = case_when(
    aversion_type == "cases_averted_direct_prop"~"Direct effects",
    aversion_type == "cases_averted_indirect_prop"~"Indirect effects")) %>%
  mutate(outcome = case_when(
    outcome == "all_cases"~"All cases",
    outcome == "symptomatic_cases"~"Symptomatic cases",
    outcome == "gp_visits"~"GP consultations",
    outcome == "hospital_cases"~"Hospital cases",
    outcome == "bed_days"~"Bed days",
    outcome == "deaths"~"Deaths"
  )) %>% 
  mutate(outcome = factor(outcome,
    levels = c("All cases", "Symptomatic cases", "GP consultations", "Hospital cases", "Bed days", "Deaths") )) %>%
  mutate(age_group_cat = factor(age_group_cat, levels = c("<6 mo", "6-11 mo", "1-4 yrs", "5-64 yrs", "65+ yrs"))) %>%
  mutate(name = factor(name, levels = c("VHR", "S", "YR", "S-catchup", "S-catchup-pid")))

p2 <- direct_df_summary_plt %>% 
  ggplot() + 
    geom_col(aes(y = outcome, x = prop, fill = age_group_cat)) + 
    facet_grid(cols = vars(aversion_type), rows = vars(name)) + 
    labs(y = "Healthcare outcome", x = "Proportion of total cases averted", fill = "Age group") + theme_bw() + 
    theme(axis.text.x = element_text(angle = 90))
  
(p1A + p1B) / p2 + plot_annotation(tag_levels = 'A')
ggsave(file = here::here("outputs", "nirsevimab", "figs", "fig0a.pdf"), heigh = 11, width = 10)

```



# Run and plot stuff

```{r}

library(tidyverse)
library(patchwork)
base_icer_temp <- load(here::here("outputs", "nirsevimab", "icer", "base_icer.RData"))
base_icer <- get(base_icer_temp) %>% mutate(icer_threshold = "20000")

lower_icer_temp <- load(here::here("outputs", "nirsevimab", "icer", "lower_icer.RData"))
lower_icer <- get(lower_icer_temp) %>% mutate(icer_threshold = "15000")

icer <- bind_rows(base_icer, lower_icer) %>%
  mutate(scale = case_when(names == "vhr"~2, names != "vhr"~1)) %>%
  mutate(names = factor(names, levels = c("vhr", "seasonal", "seasonal_and_catchup", "seasonal_and_catchup_nip"))) %>%
  mutate(names = case_when(
    names == "vhr"~"VHR",
    names == "seasonal"~"S",
    names == "seasonal_and_catchup"~"S-catchup",
    names == "seasonal_and_catchup_nip"~"S-catchup-pid"))

p1 <- icer %>% 
  filter(names == "VHR") %>%
  ggplot() + 
    geom_boxplot(aes(x = names, y = ppd, fill = icer_threshold) )
p2 <- icer %>% 
  filter(names != "VHR") %>%
  ggplot() + 
    geom_boxplot(aes(x = names, y = ppd, fill = icer_threshold) )

p1 + p2 + plot_layout(widths = c(1, 3), guides = "collect") & labs(x = "Progammes", y = "Price per dose to be cost-effective (£)", fill = "ICER threshold") &
  theme_bw()
ggsave(file = here::here("outputs", "nirsevimab", "figs", "fig1a.pdf"))

p1 <- icer %>%
  ggplot(aes(ppd, color = names, linetype = icer_threshold)) + 
  geom_hline(yintercept = 0, ) + geom_hline(yintercept = 1) + 
  geom_line(aes(y = 1 - ..y..), size = 1.5, 
    alpha = 0.7, stat = 'ecdf') + 
  scale_linetype_manual(values = c("dotted", "solid")) + 
  facet_grid(cols = vars(scale), scales = "free_x") 

g <- p1 + plot_layout(guides = "collect") &
  labs(x = "Price per dose (£)", y = "Probability that programme is cost-effective", fill = "ICER threshold", 
    linetype = "ICER threshold value (£/QALY)", color = "Intervention programme") &
  theme_bw() + theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

# plot result

library(grid)
gp <- ggplot_gtable(ggplot_build(g))
facet.columns <- gp$layout$l[grepl("panel", gp$layout$name)]
gp$widths[facet.columns] <- gp$widths[facet.columns] * c(2, 1)
grid::grid.draw(gp)
ggsave(file = here::here("outputs", "nirsevimab", "figs", "fig1b.pdf"), width = 11, height = 5)

```

# Sensitivity analysis plots

```{r}


base_icer_temp <- load(here::here("outputs", "nirsevimab", "icer", "base_icer.RData"))
base_icer <- get(base_icer_temp) %>% mutate(type = "base")

d_250_icer_temp <- load(here::here("outputs", "nirsevimab", "icer", "d_250_icer.RData"))
d_250_icer <- get(d_250_icer_temp) %>% mutate(type = "250_days")

d_360_icer_temp <- load(here::here("outputs", "nirsevimab", "icer", "d_360_icer.RData"))
d_360_icer <- get(d_360_icer_temp) %>% mutate(type = "360_days")

mo2_icer_temp <- load(here::here("outputs", "nirsevimab", "icer", "2mo_icer.RData"))
mo2_icer <- get(mo2_icer_temp) %>% mutate(type = "2mo_vac")

low_cov_icer_temp <- load(here::here("outputs", "nirsevimab", "icer", "low_cov_icer.RData"))
low_cov_icer <- get(low_cov_icer_temp) %>% mutate(type = "cov_70")

lower_icer_temp <- load(here::here("outputs", "nirsevimab", "icer", "lower_icer.RData"))
lower_icer <- get(lower_icer_temp) %>% mutate(type = "low_icer")

icer <- bind_rows(base_icer, d_250_icer, d_360_icer, mo2_icer, low_cov_icer, lower_icer) %>%
  mutate(scale = case_when(names == "vhr"~2, names != "vhr"~1)) %>%
  mutate(names = factor(names, levels = c("vhr", "seasonal", "seasonal_and_catchup", "seasonal_and_catchup_nip"))) %>%
  mutate(names = case_when(
    names == "vhr"~"VHR",
    names == "seasonal"~"S",
    names == "seasonal_and_catchup"~"S-catchup",
    names == "seasonal_and_catchup_nip"~"S-catchup-pid")) %>% filter(!is.na(names)) %>%
    group_by(type, names) %>% summarise(ppd_mean = mean(ppd))

icer %>% 
  ggplot() + 
    geom_point(aes(y = type, x = ppd_mean)) + 
      facet_wrap(vars(names), scales = "free")

```


## Fitting distributions
```{r}

library(tidyverse)
fitdist_ci <- function(pars, data, dist) {
    qs <- c(0.025, 0.5, 0.975); 1:3 %>% map_dbl(~ (dist(qs[.x],  pars[1], pars[2]) - data[.x])^2) %>% sum
}

fitdist_ci_g <- function(pars, data, dist) {
    qs <- c(0.025, 0.5, 0.975); 1:3 %>% map_dbl(~ (dist(p = qs[.x], loc = pars[1], scale = pars[2]) - data[.x])^2) %>% sum
}


require(evd)
eff_symp <- c(0.496, 0.745, 0.871)
eff_hosp <- c(-0.086, 0.621, 0.868)

par_fit_lnorm <- optim(c(10, 10), fitdist_ci, data = eff_symp, dist = qlnorm, method = "CG")
par_fit_weibull <- optim(c(10, 10), fitdist_ci, data = eff_symp, dist = qweibull, method = "CG") # best fit
par_fit_gamma <- optim(c(10, 10), fitdist_ci, data = eff_hosp, dist = qgamma, method = "CG")

par_fit_beta <- optim(c(10, 10), fitdist_ci, data = eff_symp, dist = qbeta, method = "CG")
hist(rbeta(1000,   12.453878,  6.942577) )

par_fit_gumbel <- optim(c(0, 10), fitdist_ci_g, data = eff_hosp, dist = qgumbel)
hist(rgamma(1000,   5.940192, 12.905101) )


```